%%
%% This is file `test.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% screenplay.dtx  (with options: `rider')
%% +=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=
%% 
%% Authored by and Copyright (C)2006 by
%% John Pate <johnny@dvc.org.uk>
%% http://dvc.org.uk
%% Latest version is available as:
%% http://dvc.org.uk/sacrific.txt/screenplay.zip
%% 
%% This program is free software; you can redistribute it and/or
%% modify it under the terms of the GNU General Public License as
%% published by the Free Software Foundation; either version 2 of
%% the License, or (at your option) any later version.
%% 
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% GNU General Public License for more details.
%% 
%% You should have received a copy of the GNU General Public
%% License along with this program; if not, write to the Free
%% Software Foundation, Inc., 51 Franklin St, Fifth Floor, Boston,
%% MA 02110-1301 USA
%% 
%% GPL v2 text also available as:
%% http://dvc.org.uk/gplv2.txt
%% 
%% +=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=+=
%% \CheckSum{356}
%% Test document: facsimile of title and first page
%% of http://www.oscars.org/awards/nicholl/scriptsample.pdf
%% to demonstrate veracity of class screenplay
%% see http://www.dvc.org.uk/sacrific.txt/
%% for more information on the document class.
%%
\documentclass{screenplay}[2020/03/06]
\title{The Revenge Night}
\author{Marco Grimaldo}
\address{Instituto Politecnico Nacional\\
Escuela Superior de Computo\\
Computer Animation}
\begin{document}
\coverpage
\fadein
\intslug[day]{Axayacatl Temple}
PEDRO and HERNAN talk about their currently situation in the foundry room.
\begin{dialogue}{Bernal}
lkasjdlsak
\begin{dialogue}{Pedro}
Hernando, Montesuma is dead, the mexicanos are so angry, they have removed the bridges and the food isn't enought now. What will we do?
\end{dialogue}
\begin{dialogue}{Hernan}

\end{dialogue}
Joe catches his breath as he leans against the podium at the
front of the room.
\begin{dialogue}[looking about the room]{Joe}
We are?
\end{dialogue}
\begin{dialogue}{April}
Don't be a moron.  You know we've
been invited to Austin to discuss
script format.
\end{dialogue}
\begin{dialogue}{Joe}
But why is the room empty?
\end{dialogue}
April and Joe both look out across the room~-- rows of empty
chairs and nary a person in sight.
\begin{dialogue}{April}
Okay, okay, don't panic.
\end{dialogue}
She takes three deep breaths.  Then she looks at her watch
and smiles.
\begin{dialogue}[continuing]{April}
We're an hour early.\dots  We should
rehearse.
\end{dialogue}
\begin{dialogue}{Joe}
Okay, you start.  Margins?
\end{dialogue}
\begin{dialogue}{April}
Left, 1.5 inches.  Right, 1.0
inches.  Top, 1.0 inches to the
body, 0.5 inches to the number.
Bottom, 0.5 to 1.5 inches,
depending on where the page break
comes.
\end{dialogue}
\end{document}
%% 
%% Hail Eris!  All Hail Discordia!
%%
%% End of file `test.tex'.
