%%
%% This is file `test.tex',
%% generated with the docstrip utility.
\documentclass{screenplay}[2020/03/06]
\title{The Revenge Night}
\author{Marco Grimaldo}
\address{Instituto Politecnico Nacional\\
Escuela Superior de Computo\\
Computer Animation}

\begin{document}
\coverpage
\fadein
\extslug[day]{Tenochtitlan}

\begin{dialogue}[voice - over]{Bernal}
On the night of June 30 to July 1, 1520, We, the Spanish conquerors under the orders of Hernan Cortes fled from the city of Tenochtitlán, capital of the Aztec empire. Many of them only tried, because they died that night.
\end{dialogue}

Scene changes to a flashback

\begin{dialogue}[voice - over]{Bernal}
The situation was complicated. In the absence of Hernan Cortes, Captain Pedro de Alvarado remained in command in the plaza of the Aztec capital. He decided to launch an attack to avoid uprisings. Alvarado's attack is known as the murder of the Templo Mayor. In this, between three hundred and six hundred men, women and children suffered and died.
\end{dialogue}

\intslug[day]{Axayacatl Temple}

PEDRO and HERNAN talk about melting all the gold possible, but PEDRO wants to run away that same night.

\begin{dialogue}{Pedro}
Hernando, Montesuma is dead, the mexicanos are so angry, they have removed the bridges and the food isn't enought now. What will we do?
\end{dialogue}

\begin{dialogue}{Hernan}
There is still a lot of gold to melt! All this is for the King!
\end{dialogue}

\begin{dialogue}{Pedro}
There is no time! If we die here, all the effort will have been in vain, there will be nothing left for the king.
\end{dialogue}

\extslug[day]{Tenochtitlan Bridges}

\begin{dialogue}[voice - over]{Bernal}
The natives had dismantled the access bridges to the island. We saw our deaths in the eyes and the bridges that were removed.
\end{dialogue}

\intslug[day]{Axayacatl Temple}

\begin{dialogue}[voice - over]{Bernal}
Hernan ordered built bridges for the escape, but they were very poor
\end{dialogue}

\extslug[night]{Axayacatl Temple}

\begin{dialogue}[Ordering to the army]{Hernan}
Carry as much gold as possible, separate the gold from King Carlos I of Spain!\\
Follow this order: Andres de Tapia, soldiers, horsemen and Tlaxcalans will go to the front. In the middle we will go and in the rear Pedro de Alvarado and the cavalry.
\end{dialogue}


The door opens and the soldiers begin to leave the temple in a silent way \dots

\extslug[night]{Tenochtitlan Streets}

\begin{dialogue}[Screaming]{Mexican Old Woman}
Bearded men try to run away!
\end{dialogue}

The voices, bugles, shouts and whistles of the Mexicans sound. \\
The Spaniards are persecuted and surrounded by Mexicans

\begin{dialogue}[Screaming]{Hernan}
Don't stop! The glory of God will bless us
\end{dialogue}

\extslug[night]{Tenochtitlan Bridges}

The Spanish accelerate and build bridges quickly, but some are hit by arrows from Mexicans.

\begin{dialogue}{Hernan}
Come on! For the love of God
\end{dialogue}

The Spaniards begin to place the bridges they have built, but these cannot be sustained and begin to break.

\begin{dialogue}[Looking the bridges]{Spain Soldier}
It will not resist! We are dead
\end{dialogue}

Behind Hernan a great battle is being fought \dots

\extslug[night]{Tenochtitlan Streets}

\begin{dialogue}[Screaming]{Mexican Soldier}
Let's go for that fake God's! 
\end{dialogue}

Spain and Mexicas soldiers screams are heard too loud, it's a clash of cultures.

\extslug[night]{Tenochtitlan Outskirts}

\begin{dialogue}[voice - over]{Bernal}
Only 50 percent of the army could survived, others died from Mexican arrows, swords, etc. Others just drowned.
\end{dialogue}

Hernan tired and degraded slowly approaches a tree and begins to cry.

\begin{dialogue}[Crying]{Hernan}
Can not be! We are soldiers of God.
\end{dialogue}

\end{document}

